AggregateCounts

### 2021-08-31 R/AggregateCounts.Rmd
Changed bin sizes, added jitter_dodge to plots, and made more functions for z-slices

```{r setup, include=FALSE}
library(conflicted)
library(tidyverse)
library(plotrix)#for std error
library(dplyr)
library(cowplot)
filter <- dplyr::filter
library(EBImage) #for rtiff
```

@@

#add proper labels for plots
aggregateList$Species <- factor(aggregateList$Species, levels = c("Pa", "Sa"),labels = c('P. aeruginosa','S. aureus'))
aggregateList$Condition <- factor(aggregateList$Condition, levels = c("mono", "pawt","papqsL", "paphz", "wt", "pqsL", "phz"),
                                  labels = c('Sa mono', 'Pa wt mono','pqsL mono','phz mono','wt co', 'pqsL co', 'phz co'))
aggregateList$TimePoint <- factor(aggregateList$TimePoint, levels = c("d1", "d4"),labels = c('Day 1','Day 4'))

aggregateList<-aggregateList %>% mutate(Culture = recode(Condition, 'Sa mono' = "mono", 'Pa wt mono' = "mono",'pqsL mono'= "mono",'phz mono'= "mono",'wt co'= "co", 'pqsL co'= "co", 'phz co'= "co"))
aggregateList<-aggregateList%>% mutate(Strain = recode(Condition, 'Sa mono' = "Sa", 'Pa wt mono' = "wt",'pqsL mono'= "pqsL",'phz mono'= "phz",'wt co'= "wt", 'pqsL co'= "pqsL", 'phz co'= "phz"))
#Adding the metadata
metaData <-read.csv('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/images metadata.csv', header = TRUE)
metaData<-metaData %>% select(SampleCode, mouse, Position, size, Region, Zdim, xyDim,xySize)
aggregateList<-metaData %>%  merge(aggregateList)
aggregateList$Region<-as.factor(aggregateList$Region)

@@

```{r aggregate wrangling and overview plots}
#Statistics from all aggregates
#Get aggregate summary per sample
aggregateListSummaryReplicate<-aggregateList%>% group_by(SampleCode, Species, Strain, Culture,TimePoint, Condition, Replicate,Region) %>% 
  summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), seAggSize = std.error(Size), maxSize = max(Size), minSize = min(Size)) %>%
  ungroup() %>% mutate(RatioMaxTotal = maxSize/biomass)

#Plot agg summary per sample
#####
ggplot()+ 
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= meanAggSize, color = Strain,shape = "MeanSize"),size = 3, height = 0, width = .3)+
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= maxSize, color = Strain, shape = "MaxSize"),size = 3, height = 0, width = .3)+
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= biomass, color = Strain, shape = "TotalBiomass"),size = 3, height = 0,width= .3)+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_grid(Species~Culture, scales = "free", space = "free") +
  ggtitle('Mean size and largest aggregate and total biomass per sample')+
  labs(x = "",y = bquote(paste("Volume (", mu*"m"^3*")")))+
  scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
  scale_color_brewer(palette = "Set1")+
  theme_cowplot()+
  panel_border() +
  theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
#####
#Plot only biomass per Sample
PlotBiomasPerSample<-function(df){
ggplot()+ 
    #this is for multiple conditions
  #geom_point(data = df, aes(x = Strain, y= biomass, shape = Region, color = Culture),size = 3, position = position_dodge(width = .6))+
  geom_point(data = df, aes(x = Culture, y= biomass, color= Species, shape = Region),size = 3, 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(1, 100000000))+
      #this is for multiple conditions  
    #facet_grid(Species~TimePoint, scales = "free", space = "free") +
    #this is for only one mutant
    facet_grid(.~TimePoint, scales = "free", space = "free") +
  ggtitle('Total biomass per sample')+
  labs(x = "",y = bquote(paste("Volume (", mu*"m"^3*")")))+
  scale_color_brewer(palette = "Set1")+
  scale_shape_manual(values=c(1, 2,0))+
  theme_cowplot()+
  panel_border() +
  theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}

PlotBiomasPerSample(aggregateListSummaryReplicate)
#plotting only Sa and pa wt in mono and co-culture
PlotBiomasPerSample(aggregateListSummaryReplicate %>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"))

#Get aggregate Summary per condition
aggregateListSummaryCondition<-aggregateListSummaryReplicate %>% group_by(Species, Strain, Culture,TimePoint, Condition, Region) %>% 
  summarise(meanAggs= mean(Aggs), meanBiomassLog = mean(log10(biomass)), SEBiomassLog = std.error((log10(biomass))), meanAggSize = mean(meanAggSize), seAggSize = std.error(meanAggSize))%>%  mutate(meanBiomass =  meanBiomassLog^10, SEBiomass = SEBiomassLog^10) 
#plot agg summary per condition
PlotBiomassPerCondition<-function(df, metric, error){
ggplot()+ 
  geom_pointrange(data = df, aes(x = Culture, y= .data[[metric]],
                                 ymax=.data[[metric]]+.data[[error]],ymin =.data[[metric]]-.data[[error]], color = Strain,shape = Region), 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(10000,1000000000))+
  facet_grid(Species~TimePoint, scales = "free", space = "free") +
  ggtitle('Mean size per condition and region')+
  labs(x = "",y = bquote(paste("Volume (", mu*"m"^3*")")))+
  #scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
  scale_color_brewer(palette = "Set1")+
    theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
          strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))
}
PlotBiomassPerCondition(aggregateListSummaryCondition,"meanBiomass", "SEBiomass")
PlotBiomassPerCondition(aggregateListSummary,"biomass")
#combining all 
PlotBiomasPerSampleAndConditionWT<-function(df1,df2){
ggplot()+ 
    geom_point(data = df1, aes(x = Culture, y= meanBiomassLog,color = Species,shape = Region), 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75), size = 4)+
  geom_point(data = df2, aes(x = Culture, y= log10(biomass), color= Species, shape = Region),size = 1, 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
    #scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(1, 100000000))+
      facet_grid(.~TimePoint, scales = "free", space = "free") +
  ggtitle('Biomass per sample')+
  labs(x = "",y = bquote(paste("Volume (log10", mu*"m"^3*")")))+
  scale_color_brewer(palette = "Set1")+
  scale_shape_manual(values=c(16, 1))+
  ylim(0,8)+
    theme_cowplot()+
  panel_border() +
  theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}
PlotBiomasPerSampleAndConditionWT(aggregateListSummaryCondition%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"),
                                aggregateListSummaryReplicate %>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"))
PlotBiomasPerSampleAndCondition<-function(df1,df2){
ggplot()+ 
    geom_point(data = df1, aes(x = Culture, y= meanBiomassLog,color = Strain,shape = Region), 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75), size = 4)+
  geom_point(data = df2, aes(x = Culture, y= log10(biomass), color= Strain, shape = Region),size = 1, 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
    #scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(1, 100000000))+
      facet_grid(Species~TimePoint, scales = "free", space = "free") +
  ggtitle('Biomass per sample')+
  labs(x = "",y = bquote(paste("Volume (log10", mu*"m"^3*")")))+
  scale_color_brewer(palette = "Set1")+
  scale_shape_manual(values=c(4,16, 1))+
  ylim(0,8)+
    theme_cowplot()+
  panel_border() +
  theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}
PlotBiomasPerSampleAndCondition(aggregateListSummaryCondition,aggregateListSummaryReplicate)

@@

#There are two ways to normalize the Bin Frequncy and Bin Biomass, per condition and per sample, so I'll do both
#First per replicate:
HistReplicate<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ 5,
                        Size<= 10 ~ 10,
                        Size<= 100    ~ 100,
                        Size<= 1000   ~ 1000,
                        Size<= 10000  ~ 10000,
                        Size<= 100000 ~ 100000,
                        Size > 100000 ~ 1000000)) %>% group_by(Species,Culture,Strain, Condition,TimePoint, Replicate)%>% 
  mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>% 
  group_by(Species,Culture,Strain, Condition,TimePoint, Replicate, LogBin)%>%
  mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
  mutate(NormalizedFrequency = BinFrequency/TotalFrequency*100, NormalizedBiomass = BinBiomass/TotalBiomass*100)

#This is weird, but I want to have the histogram above with all the data, and the one below with only the bins
HistReplicateSummary<-HistReplicate %>% 
  group_by(Species,Culture,Strain, Condition,TimePoint, Replicate, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%
  unique()%>%ungroup() %>%  group_by(Species,Culture,Condition,TimePoint, Replicate) %>% 
  mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))

#Now per condition. The difference is int the "group_by" part
HistCondition<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ 5,
                        Size<= 10 ~ 10,
                        Size<= 100    ~ 100,
                        Size<= 1000   ~ 1000,
                        Size<= 10000  ~ 10000,
                        Size<= 100000 ~ 100000,
                        Size > 100000 ~ 1000000)) %>% group_by(Species,Culture,Strain, Condition,TimePoint)%>% 
  mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>%
  group_by(Species,Culture,Strain, Condition,TimePoint,LogBin)%>%
  mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
  mutate(NormalizedFrequency = BinFrequency/TotalFrequency*100, NormalizedBiomass = BinBiomass/TotalBiomass*100)

#Summary data frame
HistConditionSummary<-HistCondition %>%
  group_by(Species,Culture,Strain, Condition,TimePoint,LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>% 
  unique()%>%ungroup() %>%  group_by(Species,Culture,Condition,TimePoint) %>% 
  mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))

>>>>

```{r setup, include=FALSE}
library(conflicted)
library(tidyverse)
library(plotrix)#for std error
library(dplyr)
library(cowplot)
filter <- dplyr::filter
library(EBImage) #for rtiff

@@

#add proper labels for plots
aggregateList$Species <- factor(aggregateList$Species, levels = c("Pa", "Sa"),labels = c('P. aeruginosa','S. aureus'))
aggregateList$Condition <- factor(aggregateList$Condition, levels = c("mono", "pawt","papqsL", "paphz", "wt", "pqsL", "phz"),
                                  labels = c('Sa mono', 'wt mono','pqsL mono','phz mono','wt co', 'pqsL co', 'phz co'))
aggregateList$TimePoint <- factor(aggregateList$TimePoint, levels = c("d1", "d4"),labels = c('Day 1','Day 4'))

aggregateList<-aggregateList %>% mutate(Culture = recode(Condition, 'Sa mono' = "mono", 'wt mono' = "mono",'pqsL mono'= "mono",'phz mono'= "mono",'wt co'= "co", 'pqsL co'= "co", 'phz co'= "co"))
aggregateList<-aggregateList%>% mutate(Strain = recode(Condition, 'Sa mono' = "Sa", 'wt mono' = "wt",'pqsL mono'= "pqsL",'phz mono'= "phz",'wt co'= "wt", 'pqsL co'= "pqsL", 'phz co'= "phz"))
aggregateList<-aggregateList%>% mutate(SaStrain = recode(Condition, 'Sa mono' = "Sa mono", 'wt mono' = "wt",'pqsL mono'= "pqsL",'phz mono'= "phz",'wt co'= "co-wt", 'pqsL co'= "co-pqsL", 'phz co'= "co-phz"))

#Adding the metadata
metaData <-read.csv('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/images metadata.csv', header = TRUE)
metaData<-metaData %>% select(SampleCode, mouse, Position, size, Region, Zdim, xyDim,xySize)
aggregateList<-metaData %>%  merge(aggregateList)
aggregateList$Region<-as.factor(aggregateList$Region)

@@

```{r aggregate wrangling and overview plots}
#Statistics from all aggregates
#Get aggregate summary per sample
aggregateListSummaryReplicate<-aggregateList%>% group_by(SampleCode, Species,SaStrain, Strain, Culture,TimePoint, Condition, Replicate,Region) %>% 
  summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), seAggSize = std.error(Size), maxSize = max(Size), minSize = min(Size)) %>%
  ungroup() %>% mutate(RatioMaxTotal = maxSize/biomass)

#Get aggregate Summary per condition
aggregateListSummaryCondNoRegion<-aggregateListSummaryReplicate %>% group_by(Species,SaStrain, Strain, Culture,TimePoint, Condition) %>% 
  summarise(meanAggs= mean(Aggs), meanBiomassLog = mean(log10(biomass)), SEBiomassLog = std.error((log10(biomass))), meanAggSize = mean(meanAggSize), seAggSize = std.error(meanAggSize))%>%  mutate(meanBiomass =  meanBiomassLog^10, SEBiomass = SEBiomassLog^10)

#Get aggregate Summary per condition and region
aggregateListSummaryCondition<-aggregateListSummaryReplicate %>% group_by(Species, SaStrain,Strain, Culture,TimePoint, Condition, Region) %>% 
  summarise(meanAggs= mean(Aggs), meanBiomassLog = mean(log10(biomass)), SEBiomassLog = std.error((log10(biomass))), meanAggSize = mean(meanAggSize), seAggSize = std.error(meanAggSize))%>%  mutate(meanBiomass =  meanBiomassLog^10, SEBiomass = SEBiomassLog^10)

#Plot agg summary per sample
#####
ggplot()+ 
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= meanAggSize, color = Strain,shape = "MeanSize"),size = 3, height = 0, width = .3)+
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= maxSize, color = Strain, shape = "MaxSize"),size = 3, height = 0, width = .3)+
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= biomass, color = Strain, shape = "TotalBiomass"),size = 3, height = 0,width= .3)+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_grid(Species~Culture, scales = "free", space = "free") +
  ggtitle('Mean size and largest aggregate and total biomass per sample')+
  labs(x = "",y = bquote(paste("Volume (", mu*"m"^3*")")))+
  scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
  scale_color_brewer(palette = "Set1")+
  theme_cowplot()+
  panel_border() +
  theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
#####
#Plot only biomass per Sample
#####
PlotBiomasPerSample<-function(df){
ggplot()+ 
    #this is for multiple conditions
  #geom_point(data = df, aes(x = Strain, y= biomass, shape = Region, color = Culture),size = 3, position = position_dodge(width = .6))+
  geom_point(data = df, aes(x = Culture, y= biomass, color= Species, shape = Region),size = 3, 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(1, 100000000))+
      #this is for multiple conditions  
    #facet_grid(Species~TimePoint, scales = "free", space = "free") +
    #this is for only one mutant
    facet_grid(.~TimePoint, scales = "free", space = "free") +
  ggtitle('Total biomass per sample')+
  labs(x = "",y = bquote(paste("Volume (", mu*"m"^3*")")))+
  scale_color_brewer(palette = "Set1")+
  scale_shape_manual(values=c(1, 2,0))+
  theme_cowplot()+
  panel_border() +
  theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}

#plotting all conditions
PlotBiomasPerSample(aggregateListSummaryReplicate)
#plotting only Sa and pa wt in mono and co-culture
PlotBiomasPerSample(aggregateListSummaryReplicate %>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"))
#####

#plot agg summary per condition#this shows both contition and replicate
#####
PlotBiomassPerCondition<-function(df, metric, error){
ggplot()+ 
  geom_pointrange(data = df, aes(x = Culture, y= .data[[metric]],
                                 ymax=.data[[metric]]+.data[[error]],ymin =.data[[metric]]-.data[[error]], color = Strain,shape = Region), 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(10000,1000000000))+
  facet_grid(Species~TimePoint, scales = "free", space = "free") +
  ggtitle('Mean size per condition and region')+
  labs(x = "",y = bquote(paste("Volume (", mu*"m"^3*")")))+
  #scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
  scale_color_brewer(palette = "Set1")+
    theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
          strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))
}

PlotBiomassPerCondition(aggregateListSummaryCondition,"meanBiomass", "SEBiomass")
#####

#Plotting mean and all samples
PlotBiomasPerSampleAndConditionWT<-function(df1,df2, df3){
ggplot()+ 
    geom_point(data = df1 %>% filter(TimePoint=="Day 4"), aes(x = Culture, y= meanBiomassLog,shape = Region), 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75), size = 4)+
  geom_point(data = df2%>% filter(TimePoint=="Day 4"), aes(x = Culture, y= log10(biomass), shape = Region),size = 1, 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
    geom_point(data = df3 %>% filter(TimePoint=="Day 4"), aes(x = Culture, y= meanBiomassLog),shape = 3,size = 4)+
    #scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(1, 100000000))+
      facet_grid(.~Species, scales = "free", space = "free") +
  ggtitle('Biomass per sample')+
  labs(x = "",y = bquote(paste("log10 Volume (", mu*"m"^3*")")))+
  scale_color_brewer(palette = "Set1")+
  scale_shape_manual(values=c(16, 1))+
  ylim(0,8)+
    theme_cowplot()+
  panel_border() +
  theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}

#WT only
PlotBiomasPerSampleAndConditionWT(aggregateListSummaryCondition%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"),
                                aggregateListSummaryReplicate %>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"), 
                                aggregateListSummaryCondNoRegion%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"))

PlotBiomasPerSampleAndCondition<-function(df1,df2, df3, species){
ggplot()+ 
    geom_point(data = df1 %>% filter(TimePoint=="Day 4") %>% filter(Species==species), aes(x = SaStrain, y= meanBiomassLog,shape = Region), 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75), size = 4)+
  geom_point(data = df2%>% filter(TimePoint=="Day 4") %>% filter(Species==species), aes(x = SaStrain, y= log10(biomass), shape = Region),size = 1, 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+ 
  geom_point(data = df3 %>% filter(TimePoint=="Day 4") %>% filter(Species==species), aes(x = SaStrain, y= meanBiomassLog), shape = 3, size = 4)+
    #scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(1, 100000000))+
      facet_grid(.~Species, scales = "free", space = "free") +
  ggtitle('Total Biomass')+
  labs(x = "",y = bquote(paste("Volume (log10", mu*"m"^3*")")))+
  scale_color_brewer(palette = "Set1")+
  scale_shape_manual(values=c(16, 1))+
  ylim(0,8)+
    theme_cowplot()+
  panel_border() +
  theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}
PlotBiomasPerSampleAndCondition(aggregateListSummaryCondition,
                                aggregateListSummaryReplicate,
                                aggregateListSummaryCondNoRegion, "S. aureus")

PlotMeanAggsPerSampleAndConditionWT<-function(df1,df2, df3){
ggplot()+ 
    geom_point(data = df1 %>% filter(TimePoint=="Day 4"), aes(x = Culture, y= meanAggs,shape = Region), 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75), size = 4)+
  geom_point(data = df2%>% filter(TimePoint=="Day 4"), aes(x = Culture, y= Aggs, shape = Region),size = 1, 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
    geom_point(data = df3 %>% filter(TimePoint=="Day 4"), aes(x = Culture, y= meanAggs),shape = 3,size = 4)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(10, 100000))+
      facet_grid(.~Species, scales = "free", space = "free") +
  ggtitle('Number of groups of bacteria')+
  labs(x = "",y = "")+
  scale_color_brewer(palette = "Set1")+
  scale_shape_manual(values=c(16, 1))+
  #ylim(0,8)+
    theme_cowplot()+
  panel_border() +
  theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}
PlotMeanAggsPerSampleAndConditionWT(aggregateListSummaryCondition%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"),
                                aggregateListSummaryReplicate %>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"), 
                                aggregateListSummaryCondNoRegion%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"))

PlotMeanAggsPerSampleAndCondition<-function(df1,df2, df3,species){
ggplot()+ 
    geom_point(data = df1 %>% filter(TimePoint=="Day 4") %>% filter(Species == species), aes(x = SaStrain, y= meanAggs,shape = Region), 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75), size = 4)+
  geom_point(data = df2%>% filter(TimePoint=="Day 4")%>% filter(Species == species), aes(x = SaStrain, y= Aggs, shape = Region),size = 1, 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
    geom_point(data = df3 %>% filter(TimePoint=="Day 4")%>% filter(Species == species), aes(x = SaStrain, y= meanAggs),shape = 3,size = 4)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(10, 100000))+
      #facet_grid(, scales = "free", space = "free") +
  ggtitle('Number of groups of bacteria')+
  labs(x = "",y = "")+
  scale_color_brewer(palette = "Set1")+
  scale_shape_manual(values=c(16, 1))+
  #ylim(0,8)+
    theme_cowplot()+
  panel_border() +
  theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}
PlotMeanAggsPerSampleAndCondition(aggregateListSummaryCondition,
                                aggregateListSummaryReplicate, 
                                aggregateListSummaryCondNoRegion, "S. aureus")

PlotMeanAggsPerSampleAndConditionPa<-function(df1,df2, df3,species){
ggplot()+ 
    geom_point(data = df1 %>% filter(TimePoint=="Day 4") %>% filter(Species == species), aes(x = Strain, y= meanAggs,shape = Region, color= Region), 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),
             fill = "black", size = 4)+
  geom_point(data = df2%>% filter(TimePoint=="Day 4")%>% filter(Species == species), aes(x = Strain, y= Aggs, shape = Region, color = Region),size = 1, fill = "black", 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
    geom_point(data = df3 %>% filter(TimePoint=="Day 4")%>% filter(Species == species), aes(x = Strain, y= meanAggs),shape = 3,size = 4)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(10, 100000))+
      facet_grid(.~Culture, scales = "free", space = "free") +
  ggtitle('Number of groups of bacteria')+
  labs(x = "",y = "")+
  #scale_color_brewer(palette = "Set1")+
  scale_color_manual(values = c("white", "black"))+
  scale_shape_manual(values=c(21, 1))+
  #ylim(0,8)+
    theme_cowplot()+
  panel_border() +
  theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}

```
```{r figures 1A,1B and 2A, 2B}
#Biomass wt
PlotBiomasPerSampleAndConditionWT(aggregateListSummaryCondition%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"),
                                aggregateListSummaryReplicate %>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"), 
                                aggregateListSummaryCondNoRegion%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"))
#Biomass Sa and mutants
PlotBiomasPerSampleAndCondition(aggregateListSummaryCondition,
                                aggregateListSummaryReplicate,
                                aggregateListSummaryCondNoRegion, "S. aureus")

PlotBiomasPerSampleAndCondition(aggregateListSummaryCondition,
                                aggregateListSummaryReplicate,
                                aggregateListSummaryCondNoRegion, "P. aeruginosa")

#Number of aggregates wt
PlotMeanAggsPerSampleAndConditionWT(aggregateListSummaryCondition%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"),
                                aggregateListSummaryReplicate %>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"), 
                                aggregateListSummaryCondNoRegion%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"))

#Number of aggregates Sa and mutants
PlotMeanAggsPerSampleAndCondition(aggregateListSummaryCondition,
                                aggregateListSummaryReplicate, 
                                aggregateListSummaryCondNoRegion, "S. aureus")

PlotMeanAggsPerSampleAndConditionPa(aggregateListSummaryCondition,
                                aggregateListSummaryReplicate, 
                                aggregateListSummaryCondNoRegion, "P. aeruginosa")
```

@@

#There are two ways to normalize the Bin Frequncy and Bin Biomass, per condition and per sample, so I'll do both
#First per replicate:
#####
HistReplicate<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ "(.5, 5]",
                        Size<= 10 ~ "(5, 10]",
                        Size<= 100    ~ "(10, 100]",
                        Size<= 1000   ~ "(100, 1000]",
                        Size> 1000  ~ paste0("(1000, ",bquote("\U221E"), ")"))) %>% 
  group_by(SampleCode)%>% 
  mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>% 
  group_by(SampleCode, LogBin)%>%
  mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
  mutate(NormalizedFrequency = BinFrequency/TotalFrequency*100, NormalizedBiomass = BinBiomass/TotalBiomass*100)

HistReplicate$LogBin <- factor(HistReplicate$LogBin, levels = c("(.5, 5]", "(5, 10]","(10, 100]", "(100, 1000]", paste0("(1000, ",bquote("\U221E"), ")")),labels = c(levels = c("(.5, 5]", "(5, 10]","(10, 100]", "(100, 1000]", paste0("(1000, ",bquote("\U221E"), ")"))))
